A Bioconductor Workflow for Processing and Analysing Spatial Proteomics Data

### 2016-12-03 bioc-workflow.tex
updates based on Kathryn's comments - up to page 17

Below, we display a short summary of the data. The data contains 
5032 proteins/features common across the 2 biological replicates
for the respective 2 x 10-plex reporter tags (20
columns/samples), along with associated feature meta-data such as
protein markers, protein description, number of quantified peptides
etc (see below).

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Fri Dec  2 19:09:16 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Fri Dec  2 19:09:16 2016 
## Subset [6725,20][5032,20] Fri Dec  2 19:09:16 2016 
## Removed features with more than 0 NAs: Fri Dec  2 19:09:16 2016 
## Dropped featureData's levels Fri Dec  2 19:09:16 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

When more than 2 datasets are to be combined and too many proteins were
not consistently assayed, leading to too many proteins being filtered
out, we suggest to implement an ensemble of classifiers voting on
protein-sub-cellular niche membership over the output of several
experiments (see section \textit{Supervised machine learning} for the
description of sub-cellular assignments).

@@

Data quality is routinely examined through visualisation to verify
that sub-cellular niches have been separated along the gradient. Based
on De Duve's principle \cite{DeDuve:1981} proteins that co-localise
exhibit similar quantitation profiles across the gradient fractions
employed. One approach that has been widely used to visualise and
inspect high throughput mass spectrometry-based proteomics data is
principal components analysis (PCA). PCA is one of many dimensionality
reduction methods, that allows one to effectively summarise
multi-dimensional data in to 2 or 3 dimensions to enable
visualisation. Very generally, the original continuous
multi-dimensional data is transformed into a set of orthogonal
components ordered according to the amount of variability that they
describe. The \texttt{plot2D} and \texttt{plot3D} methods in \Biocpkg{pRoloc} allows one to
plot the principal components (PCs) of a dataset against one another,
by default the first two components are plotted on the x- and y-axis
for the \texttt{plot2D} function, and first three components are
loaded for the \texttt{plot3D} function, respectively (the
\texttt{dims} argument can be used to plot other PCs). If
distinct clusters are observed, we assume that there is organellar
separation present in the data. Although, representing the
multi-dimensional data along a limited set of PCs does not give us a
hard quantitative measure of separation, it is extremely useful
summarising complex experimental information in one figure, to get a
simplified overview of the data.

In the code chunk below we produce a 2-dimensional PCA plot of the mouse stem cell
dataset (Figure \ref{fig:pcahl}). One point on the plot represents one
protein. We can indeed see several distinct protein clusters. We
specify \texttt{fcol = NULL}, which means not to consider any feature
variable to annotate the features (proteins) with colours. We will see
later how to use this argument to annotate the PCA plot with prior information
about sub-cellular localisation.

@@

\end{knitrout}
\caption{PCA plot of the mouse stem cell data \texttt{hl}. Each dot
  represent a single protein, and cluster of proteins represent
  proteins residing in the same sub-cellular niche. The figure on the
  right bins proteins and represent the bins density to highlight the
  presence of protein clusters. }
  \label{fig:pcahl}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{par}\hlstd{(}\hlkwc{mfrow} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{2}\hlstd{))} \hlcom{## creates a two-panel figure}
\hlstd{o} \hlkwb{<-} \hlkwd{order}\hlstd{(hl}\hlopt{$}\hlstd{Iodixonal.Density)}
\hlkwd{plotDist}\hlstd{(hl[, o],} \hlkwc{pcol} \hlstd{=} \hlstr{"#00000010"}\hlstd{)}
\hlkwd{lines}\hlstd{(}\hlkwd{colMeans}\hlstd{(}\hlkwd{exprs}\hlstd{(hl[, o])),} \hlkwc{col} \hlstd{=} \hlstr{"red"}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"b"}\hlstd{)}
\hlkwd{boxplot}\hlstd{(}\hlkwd{exprs}\hlstd{(hl[, o]),} \hlkwc{las} \hlstd{=} \hlnum{2}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=\textwidth]{figure/qcbx-1}

\end{knitrout}
  \caption{Protein profiles and distribution of channel intensities.}
  \label{fig:qcbx}
\end{figure}

@@

\subsection*{Visualising markers}
Having added a the mouse markers to our \texttt{fData} from the
\texttt{pRolocmarkers} we can now visualise these annotations along
the PCA plot using the \texttt{plot2D} function and then use the
\texttt{addLegend} function to map the marker classes to the
pre-defined colours. We also display the data along the first and
seventh PCs using the \texttt{dims} argument. Note that in these calls
to the \texttt{plot2D} function, we have omitted the \texttt{fcol}
argument and use of the default \texttt{"markers"} feature variable to
annotate the plot. We choose to display PCs 1 and 7 to illustrate that
while upper principal components explain much less variability in the
data (2.23\% for PC7, as opposed to 48.41\% for PC1), we see that the
mitochondrial (purple) and peroxisome (dark blue) clusters can be
differentiated, despite the apparent overlap in the visualisation of
the two first PCs (Figure \ref{fig:plotmarkers}).

@@

\end{knitrout}
\caption{Annotated PCA plots of the \texttt{hl} dataset, as produced
  with \texttt{plt2D} and \texttt{plot3D} (right).}
  \label{fig:plotmarkers}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Fri Dec  2 19:09:18 2016 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Fri Dec  2 19:09:19 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Fri Dec  2 19:09:18 2016 
## Added markers from  'pdres' marker vector. Fri Dec  2 19:09:19 2016 
##  MSnbase version: 2.1.4
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4359719               0.3027894               0.3807832 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6994864               0.6018155               0.4232624 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4141776               0.5871408               0.9494709 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7959998               0.7097865               0.3121881 
##         Plasma membrane              Proteasome 
##               0.7104260               0.4136511
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4359719               0.3027894               0.3807832 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6994864               0.6018155               0.4232624 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4141776               0.5871408               0.9494709 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7959998               0.7097865               0.3121881 
##         Plasma membrane              Proteasome 
##               0.7104260               0.4136511
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      86                     169                      84 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     296                     477                      93 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     124                     523 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     230                     343                      38 
##         Plasma membrane              Proteasome                 unknown 
##                     326                     158                    2058
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

Below, we display a short summary of the data. The data contains 
5032 proteins/features common across the 2 biological replicates
for the respective 2 x 10-plex reporter tags (20
columns or samples), along with associated feature meta-data such as
protein markers, protein description, number of quantified peptides
etc (see below).

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{combine}\hlstd{(hyperLOPIT2015ms3r1, hyperLOPIT2015ms3r2)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 6725 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2Y3-3 (6725 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Sat Dec  3 19:13:15 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{combined} \hlkwb{<-} \hlkwd{filterNA}\hlstd{(combined)}
\hlstd{combined}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126.1 X127N.1 ... X131.2 (20 total)
##   varLabels: Replicate TMT.Reagent ... Iodixonal.Density (5 total)
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: EntryName ProteinDescription ... ProteinCoverage2 (8
##     total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Combined [6725,20] and [6268,10] MSnSets Sat Dec  3 19:13:15 2016 
## Subset [6725,20][5032,20] Sat Dec  3 19:13:15 2016 
## Removed features with more than 0 NAs: Sat Dec  3 19:13:15 2016 
## Dropped featureData's levels Sat Dec  3 19:13:15 2016 
##  MSnbase version: 1.21.7
\end{verbatim}
\end{kframe}
\end{knitrout}

When more than 2 datasets are to be combined and too many proteins
have not been consistently assayed, leading to too many proteins being
filtered out, we suggest to implement an ensemble of classifiers
voting on protein-sub-cellular niche membership over the output of
several experiments (see section \textit{Supervised machine learning}
for the description of sub-cellular assignments).

@@

Data quality is routinely examined through visualisation to verify
that sub-cellular niches have been separated along the gradient. Based
on De Duve's principle \cite{DeDuve:1981} proteins that co-localise in
a cell, exhibit similar quantitation profiles across the gradient
fractions employed. One approach that has been widely used to
visualise and inspect high throughput mass spectrometry-based
proteomics data is principal components analysis (PCA). PCA is one of
many dimensionality reduction methods, that allows one to effectively
summarise multi-dimensional data in to 2 or 3 dimensions to enable
visualisation. Very generally, the original continuous
multi-dimensional data is transformed into a set of orthogonal
components ordered according to the amount of variability that they
describe. The \texttt{plot2D} and \texttt{plot3D} methods in
\Biocpkg{pRoloc} allows one to plot the principal components (PCs) of
a dataset against one another, by default the first two components are
plotted on the x- and y-axis for the \texttt{plot2D} function, and
first three components are loaded for the \texttt{plot3D} function,
respectively (the \texttt{dims} argument can be used to plot other
PCs). If distinct clusters are observed, we assume that there is
organellar separation present in the data. Although, representing the
multi-dimensional data along a limited set of PCs does not give us a
hard quantitative measure of separation, it is extremely useful
summarising complex experimental information in one figure, to get a
simplified overview of the data.

In the code chunk below we produce a 2-dimensional PCA plot of the
mouse stem cell dataset (Figure \ref{fig:pcahl}). Each point on the
plot represents one protein. We can indeed see several distinct
protein clusters. We specify \texttt{fcol = NULL} to ignore feature
metadata columns and not annotate any feature (protein) with a
colour. We will see later how to use this argument to annotate the PCA
plot with prior information about sub-cellular localisation.

@@

\end{knitrout}
\caption{PCA plot of the mouse stem cell data \texttt{hl}. Each dot
  represents a single protein, and cluster of proteins represent
  proteins residing in the same sub-cellular niche. The figure on the
  right bins proteins and represent the bins density to highlight the
  presence of protein clusters. }
  \label{fig:pcahl}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{par}\hlstd{(}\hlkwc{mfrow} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{2}\hlstd{))} \hlcom{## creates a two-panel figure}
\hlstd{o} \hlkwb{<-} \hlkwd{order}\hlstd{(hl}\hlopt{$}\hlstd{Iodixonal.Density)}
\hlkwd{plotDist}\hlstd{(hl[, o],} \hlkwc{pcol} \hlstd{=} \hlstr{"#00000010"}\hlstd{)}
\hlkwd{lines}\hlstd{(}\hlkwd{colMeans}\hlstd{(}\hlkwd{exprs}\hlstd{(hl[, o])),} \hlkwc{col} \hlstd{=} \hlstr{"red"}\hlstd{,} \hlkwc{type} \hlstd{=} \hlstr{"b"}\hlstd{)}
\hlkwd{boxplot}\hlstd{(}\hlkwd{exprs}\hlstd{(hl[, o]),} \hlkwc{las} \hlstd{=} \hlnum{2}\hlstd{,} \hlkwc{cex.axis} \hlstd{=} \hlnum{.7}\hlstd{)}
\end{alltt}
\end{kframe}
\includegraphics[width=\textwidth]{figure/qcbx-1}

\end{knitrout}
\caption{Protein profiles and distribution of channel intensities. The
  red dots represent the mean relative intensity for each channel. }
  \label{fig:qcbx}
\end{figure}

@@

\subsection*{Visualising markers}

Having added a the mouse markers to our \texttt{fData} from the
\texttt{pRolocmarkers}, we can now visualise these annotations along
the PCA plot using the \texttt{plot2D} function and then use the
\texttt{addLegend} function to map the marker classes to the
pre-defined colours. We also display the data along the first and
seventh PCs using the \texttt{dims} argument. Note that in these calls
to the \texttt{plot2D} function, we have omitted the \texttt{fcol}
argument and use of the default \texttt{"markers"} feature variable to
annotate the plot. We choose to display PCs 1 and 7 to illustrate that
while upper principal components explain much less variability in the
data (2.23\% for PC7, as opposed to 48.41\% for PC1), we see that the
mitochondrial (purple) and peroxisome (dark blue) clusters can be
differentiated, despite the apparent overlap in the visualisation of
the two first PCs (Figure \ref{fig:plotmarkers}).

@@

\end{knitrout}
\caption{Annotated PCA plots of the \texttt{hl} dataset, as produced
  with \texttt{plot2D}.}
  \label{fig:plotmarkers}
\end{figure}

The data can also be visualised along three PCs using the
\texttt{plot3D} function (Figure \ref{fig:plotmarkers3d}). When
produced interactively, the plot can be rotated and zoomined using the
mouse.

\begin{figure}[htb]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{plot3D}\hlstd{(hl,} \hlkwc{dims} \hlstd{=} \hlkwd{c}\hlstd{(}\hlnum{1}\hlstd{,} \hlnum{2}\hlstd{,} \hlnum{7}\hlstd{))}
\end{alltt}
\end{kframe}
\end{knitrout}
  \includegraphics[width=.55\textwidth]{./Figures/plot3d.pdf}
  \caption{Using the \texttt{plot3D} function to visualise the
    \texttt{hl} dataset along PCs 1, 2 and 7. }
  \label{fig:plotmarkers3d}
\end{figure}

@@

\begin{figure}[!ht]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{prots} \hlkwb{<-} \hlkwd{c}\hlstd{(}\hlstr{"Q8CG48"}\hlstd{,} \hlstr{"Q8CG47"}\hlstd{,} \hlstr{"Q8K2Z4"}\hlstd{,} \hlstr{"Q8C156"}\hlstd{)}
\hlstd{foi13s} \hlkwb{<-} \hlkwd{FeaturesOfInterest}\hlstd{(}\hlkwc{description} \hlstd{=} \hlstr{"13S consensin proteins"}\hlstd{,}
                             \hlkwc{fnames} \hlstd{= prots,}
                             \hlkwc{object} \hlstd{= hl)}
\hlstd{foi13s}
\end{alltt}
\begin{verbatim}
## Traceable object of class "FeaturesOfInterest"
##  Created on Sat Dec  3 19:13:17 2016 
##  Description:
##   13S consensin proteins
##  4 features of interest:
##    Q8CG48, Q8CG47, Q8K2Z4, Q8C156
\end{verbatim}
\begin{alltt}
\hlkwd{plot2D}\hlstd{(hl)}
\hlkwd{addLegend}\hlstd{(hl,} \hlkwc{cex} \hlstd{=} \hlnum{.6}\hlstd{)}
\hlkwd{highlightOnPlot}\hlstd{(hl, foi13s)}
\end{alltt}
\end{kframe}
\includegraphics[width=.8\textwidth]{figure/foi-1}

@@

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Sat Dec  3 19:13:18 2016
\begin{table}[ht]
\centering
\begin{tabular}{rrllr}
  \hline
 & Replicate & Tag & Gradient.Fraction & Iodixonal.Density \\ 
  \hline
X127C &   1 & 127C & 8 to 9 (pooled) & 11.00 \\ 
  X127C.1 &   2 & 127C & 7 to 9 (pooled) & 10.00 \\ 
   \hline
\end{tabular}
\caption{Differences in gradient fraction pooling.} 
\label{tab:pdtab}
\end{table}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{hl}
\end{alltt}
\begin{verbatim}
## MSnSet (storageMode: lockedEnvironment)
## assayData: 5032 features, 20 samples 
##   element names: exprs 
## protocolData: none
## phenoData
##   sampleNames: X126 X127N ... X131.1 (20 total)
##   varLabels: Replicate Tag Gradient.Fraction Iodixonal.Density
##   varMetadata: labelDescription
## featureData
##   featureNames: Q9JHU4 Q9QXS1-3 ... Q9Z2R6 (5032 total)
##   fvarLabels: uniprot.accession uniprot.id ... pd (27 total)
##   fvarMetadata: labelDescription
## experimentData: use 'experimentData(object)'
## Annotation:  
## - - - Processing information - - -
## Added markers from  'mrk' marker vector. Sat Dec  3 19:13:17 2016 
## Added markers from  'pdres' marker vector. Sat Dec  3 19:13:18 2016 
##  MSnbase version: 2.1.4
\end{verbatim}
\begin{alltt}
\hlkwd{getMarkers}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"pd"}\hlstd{)}
\end{alltt}
\begin{verbatim}
## organelleMarkers
##                          40S Ribosome 
##                                   106 
##                          60S Ribosome 
##                                    95 
## Endoplasmic reticulum/Golgi apparatus 
##                                   393 
##                         Mitochondrion 
##                                   525 
##                           Phenotype 1 
##                                   300 
##                           Phenotype 2 
##                                   253 
##                           Phenotype 3 
##                                   203 
##                           Phenotype 4 
##                                    74 
##                           Phenotype 5 
##                                    91 
##                       Plasma membrane 
##                                   421 
##                            Proteasome 
##                                    92 
##                               unknown 
##                                  2479
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{(ts} \hlkwb{<-} \hlkwd{orgQuants}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{=} \hlnum{.5}\hlstd{))}
\end{alltt}
\begin{verbatim}
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4365435               0.3040122               0.3854846 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6882175               0.5970631               0.4277083 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4184674               0.5929501               0.9507120 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7951351               0.7077463               0.3169610 
##         Plasma membrane              Proteasome 
##               0.7256612               0.4192384
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##               0.4365435               0.3040122               0.3854846 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##               0.6882175               0.5970631               0.4277083 
##    Extracellular matrix                Lysosome           Mitochondrion 
##               0.4184674               0.5929501               0.9507120 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##               0.7951351               0.7077463               0.3169610 
##         Plasma membrane              Proteasome 
##               0.7256612               0.4192384
\end{verbatim}
\begin{alltt}
\hlstd{hl} \hlkwb{<-} \hlkwd{getPredictions}\hlstd{(hl,} \hlkwc{fcol} \hlstd{=} \hlstr{"svm"}\hlstd{,} \hlkwc{scol} \hlstd{=} \hlstr{"svm.scores"}\hlstd{,} \hlkwc{mcol} \hlstd{=} \hlstr{"markers"}\hlstd{,} \hlkwc{t} \hlstd{= ts)}
\end{alltt}
\begin{verbatim}
## ans
##            40S Ribosome            60S Ribosome      Actin cytoskeleton 
##                      84                     171                      88 
##                 Cytosol   Endoplasmic reticulum                Endosome 
##                     295                     478                      99 
##    Extracellular matrix                Lysosome           Mitochondrion 
##                      27                     124                     520 
##     Nucleus - Chromatin Nucleus - Non-chromatin              Peroxisome 
##                     229                     345                      39 
##         Plasma membrane              Proteasome                 unknown 
##                     315                     158                    2060
\end{verbatim}
\end{kframe}
\end{knitrout}
